### 2020-09-01 cases_and_policies/rmd/cf-pindex.Rmd
Fixed titles of mask figures.

We now look at what happens when all states impose a mask mandate on
May 14th.

@@

```{r, cache=FALSE}
cfmask <- merge(cfmask, abbrv, by="state")
for (st in c("Washington","Illinois","Massachusetts")) {
  f <- cfplots(st, cfmask, data=df)
  print(f$figp +  ggtitle(sprintf("Effect of mandating masks on May 14th in %s",st)))

@@

figs <- nationalplots(maskall, cfmask, "mandating masks on May 14th\n")

>>>>

@@

```{r, cache=FALSE}
cfmask <- merge(cfmask, abbrv, by="state")
for (st in c("Washington","Illinois","Massachusetts")) {
  f <- cfplots(st, cfmask, data=df)
  print(f$figp +  ggtitle(sprintf("Effect of mandating masks on March 14th in %s",st)))

@@

figs <- nationalplots(maskall, cfmask, "mandating masks on March 14th\n")
